Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation with Real-Time Maude

### 2016-03-23 RMS/submission.tex
added related work and some comparison

>>>>

\jx{

  Using a model-based checking approach enhance the ability to check other scheduling
  algorithms.

  The chinese one:

  - the model is ideal

  - it should give a model to each task. And given different task sets, the model should be
  adjusted. But our model need only an instantiation of the task set.

  - the time domain. It uses a global integer to model the time, hence the time dense
  must be discrete. But our model use a generic time domain, which can be instantiated on
  both dense and discrete domain.
}
